\documentclass[sigconf]{acmart}

\usepackage[english]{babel}
\usepackage{blindtext}
\usepackage{subcaption}
\usepackage[]{graphicx}

% Copyright
\renewcommand\footnotetextcopyrightpermission[1]{} % removes footnote with conference info
\setcopyright{none}
%\setcopyright{acmcopyright}
%\setcopyright{acmlicensed}
%\setcopyright{rightsretained}
%\setcopyright{usgov}
%\setcopyright{usgovmixed}
%\setcopyright{cagov}
%\setcopyright{cagovmixed}

\settopmatter{printacmref=false, printccs=false, printfolios=true}

% DOI
\acmDOI{}

% ISBN
\acmISBN{}

%Conference
%\acmConference[Submitted for review to SIGCOMM]{}
%\acmYear{2018}
%\copyrightyear{}

%% {} with no args suppresses printing of the price
\acmPrice{}


\begin{document}
\title{Measurement study of DNS over IPv6: Problem and Solution}

%\titlenote{Produces the permission block, and copyright information}
%\subtitle{Extended Abstract}

\author{Linjian Song, Shengling Wang}
% \author{Firstname Lastname}
% \authornote{Note}
% \orcid{1234-5678-9012}
% \affiliation{%
%   \institution{Affiliation}
%   \streetaddress{Address}
%   \city{City} 
%   \state{State} 
%   \postcode{Zipcode}
% }
% \email{email@domain.com}

% The default list of authors is too long for headers}
\renewcommand{\shortauthors}{X.et al.}

\begin{abstract}
   Internet works on reliable naming and IP package transmission. 
   As complexity added into Internet infrastructure due to security 
   and stability consideration, some mismatch and unexpected fragility 
   are exposed. One case is in the field of DNS (DNSSEC) and IPv6. 
   There are some public evidence and concerns on IPv6 fragmentation 
   issues due to larger DNS payloads over IPv6. Different from other 
   measurement work, in this paper we proposed "glueless" measurement 
   mechanism to analyze the end-to-end users experience worldwide. 
   It is based on a live, real and global Ads system and shows that 
   the IPv6 large packet drop rate is up to 38\%. Our analysis shows 
   the combination of DNSSEC, UDP and IPv6 is really not going to work 
   very well. In the meanwhile, we advance a solution called ATR 
   (Additional Truncated Response) as a fix on DNS server which 
   requires no modification on users side (DNS resolver) and support 
   incremental deployment. We also conducted a measurement which shows 
   more than 68\% impacted users can be relieved on DNS latency and 
   failures due to large DNS response.
\end{abstract}

\maketitle

\input{body}

\bibliographystyle{ACM-Reference-Format}
\bibliography{reference}

\end{document}